### 2013-09-26 structured_prediction/paper.tex
trying to work on crf part.

\subsection{The SZLJSP Algorithm}\seclabel{dual_coordinate_descent}
\begin{algorithm*}[t]
    \caption{Shalev-Shwartz Zhang Lacoste-Julien Jaggi Schmidt Pletscher\label{alg_szljsp}}
    \begin{doublespacing}
    \begin{algorithmic}[1]
        \Require training samples $\{ (x\hoch{i}, y\hoch{i}), \dots, (x\hoch{i}, y\hoch{i})\}$, regularization parameter $C$, stopping tolerance $\epsilon$.
        \Ensure parameters $\theta$
        \State  $\displaystyle \theta_0^{\vphantom{i}}, \theta_0\hoch{i}, \bar{\theta}_0^{\vphantom{i}} \leftarrow \mathbf{0},\quad \ell_0^{\vphantom{i}}, \ell_0\hoch{i}, t \leftarrow 0 $
        \Repeat
            \State $t \leftarrow t + 1$
            \State Pick $i$ uniformly at random from $\{1, \dotsc, k\}$.
            \State Perform loss-augmented prediction on sample $i$:
            \Statex[2]   $\hat{y} \leftarrow I(x\hoch{i}, y\hoch{i}, \theta) := \displaystyle \argmax_{\hat{y}\in\mathcal{Y}} \Delta(y\hoch{i}, \hat{y}) - \theta^T [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y})]$
            \State Compute parameter and loss updates based on sample $i$:
            \Statex[2]     $\theta_s \leftarrow \frac{C}{n} \Phi(x, \hat{y})$
            \Statex[2]     $\ell_s \leftarrow \frac{C}{n} \delta(y\hoch{i}, \hat{y})$
            \State Compute optimum step size $\eta$:
            \Statex[2]    $\eta \leftarrow \frac{(\theta_t\hoch{i} - \theta_s)^T \theta_t + C (\ell_s - \ell_k\hoch{i} )}{\lVert \theta_t\hoch{i} - \theta_s \rVert^2}$ and clip to $[0, 1]$
            \State Update per-sample parameters and loss estimate:
            \Statex[2]    $\theta_{t+1}\hoch{i} \leftarrow (1 - \eta) \theta_{t+1}\hoch{i} + \eta \theta_s$
            \Statex[2]    $\ell_{t+1}\hoch{i} \leftarrow (1 - \eta) \theta_{t+1}\hoch{i} + \eta \ell_s$
            \State Update global parameters and loss estimate:
            \Statex[2]   $\theta_{t+1} \leftarrow \theta_{t+1} + \theta_{t}\hoch{i} - \theta_{t+1}\hoch{i}$
            \Statex[2]   $\ell_{t+1} \leftarrow \ell_{t+1} + \ell_{t}\hoch{i} - \ell_{t+1}\hoch{i}$
            \State Compute the weighted running average:
            \Statex[2] $\bar{\theta}_{t+1} = \frac{k}{k + 2} \bar{\theta}_k + \frac{2}{k + 2}\theta_{k+1}$
        \Until $(\theta - \theta_s)^T\theta - \ell + \ell_s \leq \epsilon$
        \Statex where $\theta_s$ and $\ell_s$ are recomputed over the whole dataset.
    \end{algorithmic}
    \end{doublespacing}
\end{algorithm*}

@@

\section{CRFs for Semantic Segmentation}\seclabel{semantic_segmentation}
%
Structured models based on factor graphs, as described in \Secref{factor_graphs} are often
referred to as Conditional Random Fields (CRFs), pointing to their
probabilistic interpretation.
Conditional Random Fields have been established as an important tool in many
areas of computer vision. Applications include dense stereo, optical flow, 
inpainting, de-noising, image editing, low-level segmentation and semantic segmentation.

Most conditional random fields only apply unary and pairwise potential functions. In this case, FIXME equation 4.4
becomes
\begin{equation}\eqlabel{energy_crf}
    g(x, y) = \sum_{v \in V} \psi_v(x, y_v) + \sum_{(v, w) \in E} \psi_{v,w}(x, y_{v}, y_{w}).
\end{equation}
Here $V$ enumerates variables, and $E\subset V \times V$ is a set of edges,
representing pairwise factors.

There are broadly two types of models that are used: models in which each pixel
in an image is represented as a variable, and models in which pixels are first
grouped together into superpixels and each superpixel is represented as a variable.
In pixel-based CRFs edges are usually introduced between adjacent pixels, that is using
either 4-neighborhoods or 8-neighborhoods. Superpixel-based approaches introduce
edges between adjacent superpixels, that is those that share a boundary.
%TODO images of superpixels!
By nature, both approaches create graphs with a large number of loops. This
complicates prediction and learning, and is the central topic of
Chapter~\ref{ch:exact_learning}.

The motivation for using superpixels is that it is often easy to group nearby
pixels that belong to the same object just based on local color or texture cues.
While it is hard to even define what makes a sensible segmentation of an image,
it is much easier to define, and also to compute an \emph{over-segmentation}.
The only requirement for an over-segmentation is that each segment only
contains pixels belonging to the same entity.

@@

We use the SLIC~\citep{achanta2012slic} algorithm to create superpixel for all
our experiments.  It has been shown to provide competative results with a
minimum of computational complexity.  Algorithmically, SLIC simply computes a
$k$-means clustering over pixels. Each pixels is represented as 5D point, using
three color channels and the $x$ and $y$ coordinates in the image.  In a
post-processing step, small segments are removed. To make clustering of so many
points feasible, the search for the nearest cluster in $k$-means is restricted
to a local neighborhood in the image.

% about algorithms, slic?
% hierarchical\dots has superpixels and pixels?

% submodular/non-submodular? higher order?

Conditional random fields were first used in the context of semantic
segmentation by \citet{he2004multiscale}.  Who used contrastive divergence for
learning parameters. Many other early models, such as the one of
\citet{shotton2006textonboost}, did not learn parameters at all, but used
\emph{contrast-sensitive Potts potential}. These potentials have a smoothing
effect over labels by encouraging neighboring variables to take the same value.
The penalty for taking different values is dependent on color contrast between
the pixels.

This smoothing approach was improved upon by \citet{kohli2009robust}, who
introduces higher order potentials to enforce label consistency within larger
regions. Later, \citet{ladicky2009associative} proposed a hierarchical model,
including the higher order potentials of \citet{kohli2009robust}, and
additional lateral and hierarchical connections. A similar approach, using
superpixels as the finest resolution, and additionally modelling object class
coocurrences was suggested by \citet{gonfaus2010harmony}.  However, all these
models did not learn the potentials of the CRF model in a principled manner.
The above approaches all learned unary potentials using a non-structured
approach, for example SVMs or boosting, and then set pairwise and higher order
potentials in the model by hand.

@@

%TODO where does that leave us now?
In Chapter~\ref{ch:exact_learning} and Chapter~\ref{ch:nyu}, we investigate
superpixel-based conditional random fields learned using structural support
vector machines. The emphasis of Chapter~\ref{ch:exact_learning} is on
understanding the learning, and how to cope with the complexity of inference in
loopy models, while Chapter~\ref{ch:nyu} extends the approach to RGB-D images
and shows how we can learn spatial relations using parametric pairwise
potentials.

>>>>

\subsection{The SZLJSP Algorithm}\seclabel{dual_coordinate_descent}
\begin{algorithm}[tp]
    \caption{Shalev-Shwartz Zhang Lacoste-Julien Jaggi Schmidt Pletscher\label{alg_szljsp}}
    \begin{doublespacing}
    \begin{algorithmic}[1]
        \Require training samples $\{ (x\hoch{i}, y\hoch{i}), \dots, (x\hoch{i}, y\hoch{i})\}$, regularization parameter $C$, stopping tolerance $\epsilon$.
        \Ensure parameters $\theta$
        \State  $\displaystyle \theta_0^{\vphantom{i}}, \theta_0\hoch{i}, \bar{\theta}_0^{\vphantom{i}} \leftarrow \mathbf{0},\quad \ell_0^{\vphantom{i}}, \ell_0\hoch{i}, t \leftarrow 0 $
        \Repeat
            \State $t \leftarrow t + 1$
            \State Pick $i$ uniformly at random from $\{1, \dotsc, k\}$.
            \State Perform loss-augmented prediction on sample $i$:
            \Statex[2]   $\hat{y} \leftarrow I(x\hoch{i}, y\hoch{i}, \theta) := \displaystyle \argmax_{\hat{y}\in\mathcal{Y}} \Delta(y\hoch{i}, \hat{y}) - \theta^T [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y})]$
            \State Compute parameter and loss updates based on sample $i$:
            \Statex[2]     $\theta_s \leftarrow \frac{C}{n} \Phi(x, \hat{y})$
            \Statex[2]     $\ell_s \leftarrow \frac{C}{n} \delta(y\hoch{i}, \hat{y})$
            \State Compute optimum step size $\eta$:
            \Statex[2]    $\eta \leftarrow \frac{(\theta_t\hoch{i} - \theta_s)^T \theta_t + C (\ell_s - \ell_k\hoch{i} )}{\lVert \theta_t\hoch{i} - \theta_s \rVert^2}$ and clip to $[0, 1]$
            \State Update per-sample parameters and loss estimate:
            \Statex[2]    $\theta_{t+1}\hoch{i} \leftarrow (1 - \eta) \theta_{t+1}\hoch{i} + \eta \theta_s$
            \Statex[2]    $\ell_{t+1}\hoch{i} \leftarrow (1 - \eta) \theta_{t+1}\hoch{i} + \eta \ell_s$
            \State Update global parameters and loss estimate:
            \Statex[2]   $\theta_{t+1} \leftarrow \theta_{t+1} + \theta_{t}\hoch{i} - \theta_{t+1}\hoch{i}$
            \Statex[2]   $\ell_{t+1} \leftarrow \ell_{t+1} + \ell_{t}\hoch{i} - \ell_{t+1}\hoch{i}$
            \State Compute the weighted running average:
            \Statex[2] $\bar{\theta}_{t+1} = \frac{k}{k + 2} \bar{\theta}_k + \frac{2}{k + 2}\theta_{k+1}$
        \Until $(\theta - \theta_s)^T\theta - \ell + \ell_s \leq \epsilon$
        \Statex where $\theta_s$ and $\ell_s$ are recomputed over the whole dataset.
    \end{algorithmic}
    \end{doublespacing}
\end{algorithm}

@@

\section{Conditional Random Fields for Semantic Segmentation}\seclabel{semantic_segmentation}
%
\subsection{Fundamentals of Conditional Random Fields}
Structured models based on factor graphs, as described in \Secref{factor_graphs} are often
referred to as Conditional Random Fields (CRFs), pointing to their
probabilistic interpretation.
CRFs have been established as an important tool in many areas of computer
vision. Applications include dense stereo, optical flow, inpainting,
denoising, image editing, low-level segmentation and semantic segmentation.

Most conditional random fields only apply unary and pairwise potential
functions. In this case, \Eqref{log_factor_graph} becomes
\begin{equation}\eqlabel{energy_crf}
    g(x, y) = \sum_{v \in V} \psi_v(x, y_v) + \sum_{(v, w) \in E} \psi_{v,w}(x, y_{v}, y_{w}).
\end{equation}
Here $V$ enumerates variables and $E\subset V \times V$ is a set of edges which
represent pairwise factors.

There are broadly two types of models that are used: models in which each pixel
in an image is represented as a variable, and models in which pixels are first
grouped together into superpixels and each superpixel is represented as a
variable.  In pixel-based CRFs edges are usually introduced between adjacent
pixels, that is using either 4-neighborhoods or 8-neighborhoods.
Superpixel-based approaches introduce edges between adjacent superpixels, that
is those that share a boundary. \Figref{superpixel_illustration} shows a
sample image together with extracted superpixels and the neighborhood graph.

By nature, models over pixels and models over superpixels create graphs with a
large number of loops. This complicates prediction and learning, and is the
central topic of Chapter~\ref{ch:exact_learning}.

The motivation for using superpixels is that it is often easy to group nearby
pixels that belong to the same object just based on local color or texture cues.
While it is hard to even define what makes a sensible segmentation of an image,
it is much easier to define an \emph{over-segmentation}.
The only requirement for an over-segmentation is that each segment only
contains pixels belonging to the same entity.

@@

% hierarchical\dots has superpixels and pixels?

% submodular/non-submodular? higher order?
\subsection{Previous Work}
Conditional random fields were first used in the context of semantic
segmentation by \citet{he2004multiscale}.  Who used contrastive divergence for
learning parameters. Many other early models, such as the one of
\citet{shotton2006textonboost}, did not learn parameters at all, but used
\emph{contrast-sensitive Potts potential}. These potentials have a smoothing
effect over labels by encouraging neighboring variables to take the same value.
The penalty for taking different values is dependent on color contrast between
the pixels.

This smoothing approach was improved upon by \citet{kohli2009robust}, who
introduces higher order potentials to enforce label consistency within larger
regions. Later, \citet{ladicky2009associative} proposed a hierarchical model
over pixels and superpixels, including the higher order potentials of
\citet{kohli2009robust} and additional lateral and hierarchical connections. A
similar approach, using superpixels as the finest resolution, and additionally
modelling object class coocurrences was suggested by
\citet{gonfaus2010harmony}.  However, all these models did not learn the
potentials of the CRF model in a principled manner.  The above approaches all
learned unary potentials using a non-structured approach, for example SVMs or
boosting, and then set pairwise and higher order potentials in the model by
hand.

@@

\subsection{Data, Features and Superpixels}
When evaluating learning algorithms in Chapter~\ref{ch:evaluation} and
Chapter~\ref{ch:exact_learning} we use the well-established Pascal VOC 2010 and
MSRC-21 datasets, shown in the introduction in \Figref{pascal_msrc}.
As we focus on the learning algorithms in these chapters, we use features for
unary potentials from the literature.

For both datasets we use the TextonBoost class probablities provided by
\citet{krahenbuhl2012efficient}. For the Pascal VOC dataset, the potentials
provided by \citet{krahenbuhl2012efficient} also include the responses of
object detectors~\citet{}, to better capture the complex object classes.
We average the potentials inside superpixels and use the resulting feature
as input to our unary potentials.
For the MSRC-21 dataset, we compute TextonBoost on two different scales, as
suggested by \citet{mottaghianalyzing}. We additionally extract SIFT and color descriptors and create
bag-of-word descriptors for each superpixel. Following the approach of
\citet{lucchi2011spatial} we augment these with a global bag-of-word descriptor
for each image. We train a linear SVM using an approximation to the additive
$\chi^2$ kernel~\citet{vedaldi2010efficient} and use the response as an
additional input to our CRF\@. This \emph{piecewise training} simplifies
learning and was found to have little effect on
accuracy~\citet{nowozin2010parameter}. In total, there are $63$ features
for the MSRC-21 dataset, $21$ for each scale of TextonBoost and an additional
$21$ for the bag-of-word model using an SVM.

We use the SLIC~\citep{achanta2012slic} algorithm to create superpixel for all
our experiments.  It has been shown to provide competative results with a
minimum of computational complexity.  Algorithmically, SLIC simply computes a
$k$-means clustering over pixels. Each pixels is represented as 5D point, using
three color channels and the $x$ and $y$ coordinates in the image.  In a
post-processing step, small segments are removed. To make clustering of so many
points feasible, the search for the nearest cluster in $k$-means is restricted
to a local neighborhood in the image. The superpixels shown in
\Figref{superpixels_illustration} are computed using SLIC.
